
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2020_assignment8.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```




-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19.  

```{r}
install.packages("gganimate")
install.packages("gifski")
```


```{r}
choose.files()
global<-read_csv("https://covid19.who.int/WHO-COVID-19-global-data.csv")

library(lubridate)
global$month <- month(global$Date_reported)
d1<- global %>% group_by(Date_reported,Country_code) %>% summarise(mean=mean(Cumulative_deaths))
d2<- d1 %>% group_by(Date_reported) %>% mutate(rank=rank(-mean)) %>% ungroup()
d3<- d2 %>% filter(rank <=10)

bar<-d3 %>% ggplot(aes(x=rank, y=mean,group=Country,fill=Country,label=Country))+
  geom_col()+
  geom_text(aes(y=mean,label=Country),hjust=1.4)+
  coord_flip(clip="off",expand=FALSE)+
  scale_x_reserve()+
  labs(title='Month {closest_month}',x='',y='Total number of deaths',fill='Country')+theme(plot.title=element_text(hjust=1,size=22),axis.ticks.y=element+blank(),axis.text.y=element+blank())+
  transition_Country(month)+
  ease_aes("cubic-in-out")

animate(bar,nframes=400,fps=1)


```


2. Make another bar race using that dataset.  

```{r}

```


3. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar racev from ones in the slides. 
```{r}
library(gganimate)
library(ggplot2)
library(tidyverse)
library(knitr)
choose.files()
states<-"C:\\Users\\student\\Desktop\\MAT 421\\all-states-history (1).csv"

s1<- states %>%
  filter(state %in% c('CO','WA'),
         month>5)%>%
  group_by(month,state) %>%
  summarise(mean= mean(positive))
kable(s1)
```


