***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2020_assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard under Assignment 3. 

-------

Problems
-------
 \

1. Use `read.csv` to import the Covid19 data from WHO: [link](https://covid19.who.int/WHO-COVID-19-global-data.csv)

```{r}
df<-read.csv("https://covid19.who.int/WHO-COVID-19-global-data.csv")
View(df)
names(df)
```


2. How many columns and rows the data have? How many categorical variables the data have?

```{r}
dim(df)
```

```{r}
str(df)
```

3. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?

```{r}
sum(is.na(df))
```

```{r}
colSums(is.na(df))
```


4. Correct the types of the variables that are mismatched type.

```{r}
str(data)
```

```{r}
library(lubridate)
```

```{r}
df$ï..Date_reported<-ymd(df$ï..Date_reported)
class(df$ï..Date_reported)


```

5. Find the daily average number of cases globally.

```{r}
mean(df$New_cases)
```


6. Find the maximum cases a day.  

```{r}
max(df$New_cases)
```


7. Which country at which date has the maximum number of cases a day? *Hint:  use the `which.max` function to find the index of the row that contains the maximum number of cases. Then from the row index, find that country and the date. * 

```{r}
which.max(df$New_cases)
df[17924,]
```

8.  How many WHO's region there are in the data?

```{r}
length(summary(df$WHO_region))
```


9.  Find the daily average cases in EUROPE. Find the daily average cases by regions.
```{r}
#Daily average cases in Europe
mean(df[df$WHO_region=='EURO',]$New_cases)
```

```{r}
#Daily average cases by regions
by(df$New_cases,df$WHO_region,mean)
```


10. Find the daily average number of cases in the US in the last 5 days. 

```{r}
d1 = df[(df$Country_code=='US') & (Sys.Date()- df$ï..Date_reported<5),]

mean(d1$New_cases,na.rm = TRUE)
```


11. Which day of the week has the most number of cases in South East Asia (SEARO region)?

```{r}
df$weekday <- wday(df$ï..Date_reported)
df2<- df[df$WHO_region=='SEARO',]
by(df2$New_cases,df2$weekday,mean)
```

